Understanding the impact of electronically-delivered parenting advice

### 2019-02-08 paper/cogsci2019/cogsci2019.Rmd
integrated lexical diversity graphs for both Exp 1 and Exp 2

### Participants. 
60 infants aged 6-24 months and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
[include specific demo info here?] - good to include now, and we can comment it out if it's too much (the full report/paper will have it)

@@

Participants were randomly assigned to an Activity Video condition or No-Video Control condition. 
Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
Parents also completed the Parenting Attitudes Questionnaire (PAQ). 
The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

### Joint Attention Coding Procedure.
Video of each session was coded for episodes of joint attention using Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. % report reliability

@@

```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))

@@

# report table with mtld_means _sds

@@

```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
ms_tok <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "tokens")

@@

@@

@@

```{r, echo=F}
e2path = "../../parenting_obs_e2/"
#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2d <- read.csv(paste(e2path,"MTLD_HDD.csv",sep=''), header=TRUE) 
```

### Participants. 
84 infants aged 12-24 months and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. [specific demo info]

@@

```{r e2TTR, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "How to do subfigures?"}
img <- png::readPNG("figs/e2_TTR.png")
grid::grid.raster(img)
```

```{r e2MTLD, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/e2_MTLD.png")
grid::grid.raster(img)
```

@@

@@

## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

>>>>

lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))
```

### Participants. 
`r nrow(d)` infants aged 6-24 months and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
*INCLUDE FULL DEMOGRAPHIC INFO*

@@

Participants were randomly assigned to either the Activity *Video* condition or the No-Video *Control* condition. 
Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
Parents also completed the Parenting Attitudes Questionnaire (PAQ). 
The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. *REPORT RELIABILITY*

@@

```{r, e1-lexdiv-regressions, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
maximal_mod <- lmer(MTLD ~ condition + age + gender + parent_ed + (1| video), data = lmer_data)
summary(maximal_mod)

# predict word tokesn
tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1| video), 
                         data = lmer_data)
summary(tokens_mod)

# predict word types
types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1| video), 
                         data = lmer_data)
summary(types_mod)
```

```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))

# all at once, but there are NAs in SD cols ?
e1 <- d %>% group_by(Condition) %>%
  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
            types=mean(types), types.sd=sd(types),
            tokens = mean(tokens), tokens.sd=sd(tokens))

@@

# report table with mtld_means

@@

```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
ms_tok <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "tokens")

@@

```{r, e1-effect-size, echo=F}
cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
```

@@

## Discussion

Both the number of tokens and types are higher in the experimental condition, while lexical diversity (Type/Token ratio) is higher in the control condition. 
Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
Demographics and PAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).

@@

```{r, echo=F}
e2path = "../../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))

### Participants. 
`r nrow(d)` infants aged 12-24 months and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. [specific demo info]

@@

@@

```{r e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
ms_lex <- d %>% group_by(Condition) %>%
  multi_boot_standard(col="TTR") 
ttr_mean <- d%>% group_by(Condition)%>%
  summarise(mean=mean(TTR), sd=sd(TTR))

e2ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + ylim(0.0, 0.6) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("TTR") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

ms_lex <- d %>% group_by(Condition) %>%
  multi_boot_standard(col="MTLD") 
mltd_mean <- d %>% group_by(Condition)%>%
  summarise(mean = mean(MTLD), sd=sd(MTLD))

e2mtld <- ggplot(ms_lex, aes(x = Condition, y = mean, fill = Condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

multiplot(e2ttr, e2mtld, cols=2)
```

```{r e2token-type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
ms_tok <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "tokens")

e2tokens <- ggplot(ms_tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

ms_typ <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "types")

e2types <- ggplot(ms_typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

multiplot(e2tokens, e2types, cols=2)
```

@@

### 2019-02-08 paper/cogsci2019/cogsci2019.tex
integrated lexical diversity graphs for both Exp 1 and Exp 2

60 infants aged 6-24 months and their parents participated in a museum
in northern California. We included infants who were exposed to English
at least 50 percent of the time or who were exposed less but whose
participating parent reported that they primarily speak English with
their child at home. {[}include specific demo info here?{]} - good to
include now, and we can comment it out if it's too much (the full
report/paper will have it)

@@

Participants were randomly assigned to an Activity Video condition or
No-Video Control condition. Participants in the Activity Video condition
were assigned to one of the two videos available for their child's age
group. The No-Video Control condition was yoked to the Activity Video
condition such that for every participant in the Activity Video
condition who saw a particular video and received the associated props,
a participant in the No-Video Control condition received the same props
but did not watch the corresponding video. Parents also completed the
Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
attitudes about parenting and child development along three dimensions:
rules and respect, early learning, and affection and attachment.

@@

Video of each session was coded for episodes of joint attention using
Datavyu software. The video taken at floor level was coded by default,
but the other video was referred to if the participants were not visible
or if there was a technological error with the first camera. For each
participant we coded for episodes of coordinated joint attention,
episodes of passive joint attention, and parental bids for joint
attention. We defined parental bids for joint attention as any attempt
to initiate joint attention (i.e label, point, or otherwise draw
attention to an object) that does not result in passive or coordinated
joint attention. If more than 3 seconds elapsed between bids, they were
coded as separate attempts. An episode of joint attention was considered
passive if both participants visually focused on an object for a minimum
of 3 seconds but the child did not acknowledge the parent. If either
participant looked away from the object for less than 3 seconds and then
returned to the same object it was considered part of the same period of
joint attention. Episodes joint attention were considered coordinated if
both participants visually focused on an object for a minimum of 3
seconds and at some point in the interaction the child indicated
awareness of interaction with some overt behavior toward the parent.
This could be looks to the parent's face, gestures, vocalizations, or
turn-taking. If either participant looked away for less than 3 seconds
and then returned to the same object, it was coded as part of the same
period of joint attention. A second coder independently coded a third of
the videos (i.e., 20 of the 60 videos, approximately equally distributed
across ages) to establish reliability. \% report reliability

@@

@@

{\centering \includegraphics{figs/e2TTR-1}

@@

\caption[How to do subfigures?]{How to do subfigures?}\label{fig:e2TTR}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics{figs/e2MTLD-1}

@@

\caption[One column image]{One column image.}\label{fig:e2MTLD}
\end{figure}
\end{CodeChunk}

@@

\section{Discussion}\label{discussion}

@@

\subsection{Tables}\label{tables}

Number tables consecutively; place the table number and title (in 10
point) above the table with one line space above the caption and one
line space below it, as in Table 1. You may float tables to the top or
bottom of a column, set wide tables across both columns.

You can use the xtable function in the xtable package.

>>>>

59 infants aged 6-24 months and their parents participated in a museum
in northern California. We included infants who were exposed to English
at least 50 percent of the time or who were exposed less but whose
participating parent reported that they primarily speak English with
their child at home. \emph{INCLUDE FULL DEMOGRAPHIC INFO}

@@

Participants were randomly assigned to either the Activity \emph{Video}
condition or the No-Video \emph{Control} condition. Participants in the
Activity Video condition were assigned to one of the two videos
available for their child's age group. The No-Video Control condition
was yoked to the Activity Video condition such that for every
participant in the Activity Video condition who saw a particular video
and received the associated props, a participant in the No-Video Control
condition received the same props but did not watch the corresponding
video. Parents also completed the Parenting Attitudes Questionnaire
(PAQ). The PAQ measures parents' attitudes about parenting and child
development along three dimensions: rules and respect, early learning,
and affection and attachment.

@@

The video of each session was manually coded for episodes of joint
attention using the Datavyu software. The video taken at floor level was
coded by default, but the other video was referred to if the
participants were not visible or if there was a technological error with
the first camera. For each participant we coded for episodes of
coordinated joint attention, episodes of passive joint attention, and
parental bids for joint attention. We defined parental bids for joint
attention as any attempt to initiate joint attention (i.e label, point,
or otherwise draw attention to an object) that does not result in
passive or coordinated joint attention. If more than 3 seconds elapsed
between bids, they were coded as separate attempts. An episode of joint
attention was considered passive if both participants visually focused
on an object for a minimum of 3 seconds but the child did not
acknowledge the parent. If either participant looked away from the
object for less than 3 seconds and then returned to the same object it
was considered part of the same period of joint attention. Episodes
joint attention were considered coordinated if both participants
visually focused on an object for a minimum of 3 seconds and at some
point in the interaction the child indicated awareness of interaction
with some overt behavior toward the parent. This could be looks to the
parent's face, gestures, vocalizations, or turn-taking. If either
participant looked away for less than 3 seconds and then returned to the
same object, it was coded as part of the same period of joint attention.
A second coder independently coded a third of the videos (i.e., 20 of
the 60 videos, approximately equally distributed across ages) to
establish reliability. \emph{REPORT RELIABILITY}

@@

\subsection{Discussion}\label{discussion}

Both the number of tokens and types are higher in the experimental
condition, while lexical diversity (Type/Token ratio) is higher in the
control condition. Parents may be relatively more repetetive in the
experimental condition since they are attempting to stick to a specific
prescribed task, but they talk more overall. Demographics and PAQ do not
interact with condition, but there is a marginal effect of RR score on
lexical diversity (lower diversity for higher RR scores), and marginal
effects of parent education on word types and tokens (more types and
tokens for higher parent education).

@@

{\centering \includegraphics{figs/e2lexdiv-1}

@@

\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2.}\label{fig:e2lexdiv}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics{figs/e2token-type-1}

@@

\caption[Mean number of word types and word tokens by condition in Experiment 2]{Mean number of word types and word tokens by condition in Experiment 2.}\label{fig:e2token-type}
\end{figure}
\end{CodeChunk}

@@

\section{Discussion}\label{discussion-1}

@@
